---
title: "Type coercion"
author: "Naomi Ekas"
output: github_document
---

## Exercise 1

-   `c(1, 1L, "C")`

my guess is R changes all three to a character
I was correct!

```{r}
c(1, 1L, "C")
```
## Exercise 2 
1 is a double
1L is an integer
"c" is a character

```{r}
1
1L
"C"
```

## Exercise 3

all of these will come out as character
```{r}
typeof(c(1, 1L, "C"))
```
## Exercise 4
-   `c(1L / 0, "A")`
all of these will be a character

```{r}
c(1L / 0, "A")
```
## Exercise 5
integer
double
character
character
```{r}
typeof(1L)
typeof(0)
typeof(1L/0)
typeof("A")
```
I was wrong on the double

## Exercise 6
all will be Characters
```{r}
typeof(c(1L / 0, "A"))
```
## Exercise 7
-   `c(1:3, 5)`

```{r}
c(1:3, 5)
```
## Exercise 8
```{r}
typeof(1:3)
typeof(5)
```
## Exercise 9
```{r}
typeof(c(1:3, 5))
```
## Exercise 10
-   `c(3, "3+")`

```{r}
c(3, "3+")
```
## Exercise 11
```{r}
typeof(3)
typeof("3+")
```
## Exercise 12
```{r}
#typeof(c(3, "3+"))
```

## Exercise 13
-   `c(NA, TRUE)`

```{r}
c(NA, TRUE)
```
## Exercise 14
logical
```{r}
typeof(NA)
typeof(TRUE)
```
## Exercise 15
```{r}
typeof(c(NA, TRUE))
```
